---
title: "Rhdf5client2 Vignette"
author: "Sam"
date: "9/1/2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rhdf5client2)
```

## Source

An object of type Source is a HDFGroup server running on a machine. The 
constructor requires the endpoint and server type, either `h5serv` or `hsds`. 
If the type is not specified, the server will be assumed to be `hsds`

```{r}
test_ipaddr <- '34.202.237.217'    # today's address for test machine
test_endpoint <- paste0('http://', test_ipaddr, ':5000')
src.hsds <- Source('http://hsdshdflab.hdfgroup.org')
src.test <- Source(test_endpoint, 'h5serv')
src.chan <- Source('http://h5s.channingremotedata.org:5000', 'h5serv')
```

The routine `domains` is provided for inspection of the server hierarchy.
This is the hierarchy that maps approximately to the directory structure of
the server file system. The purpose of this routine is to assist the user
in locating HDF5 files. 

The user needs to know the root domain of the server. This information 
should be published with the endpoint. For an h5serv server, the default 
`hdfgroup.org` is a good guess, because this value is preconfigured and 
there is not often a reason to wish to change it. 

```{r}
domains(src.chan)
domains(src.chan, 'public/hdfgroup/org')
```

```{r}
domains(src.test, 'data/hdfgroup/org')
domains(src.test, 'subdira/data/hdfgroup/org')
```

For an hsds server, the root domain could be anything, so the administrator
has to publish it.

```{r}
domains(src.hsds, '/home/jreadey')
domains(src.hsds, '/home/jreadey/HDFLabTutorial')
```

## File

An object of class File represents a HDF5 file. The object is constructed 
by providing a source and a file domain. (TODO: if the domain is not a 
real file domain, this crashes with an unhelpful error message.)

```{r}
f0 <- File(src.hsds, '/home/spollack/testzero.h5')
f1 <- File(src.chan, 'tenx_100k_sorted.h5s.channingremotedata.org')
f2 <- File(src.test, 'fileone.subdira.data.hdfgroup.org')
```

The function `listDatasets` lists the datasets in a file.

```{r}
listDatasets(f0)
listDatasets(f1)
listDatasets(f2)
```

## Dataset

Construct a Dataset object from a File and a dataset path.

```{r}
d0 <- Dataset(f0, '/grpA/grpAB/dsetX')
d1 <- Dataset(f1, '/assay001')
d2 <- Dataset(f2, '/grpB/grpC/dataC')
```

The fundamental data retrieval method is `getData`. It's argument is a
vector of slices of type `character`. Valid slices are `:` (all indices), 
`1:10` (indices 1 through 10 inclusive), `:10` (same as `1:10`), `5:` 
(from 5 to the maximum value of the index) and `2:14:4` (from 2 to 14 
inclusive in increments of 4.)

Note that the slice should be passed in R semantics. I.e., 1 signifies
the first index and the last element is included in the slice. (Internally,
rhdf5client2 converts to Python semantics, in which the first index is 0 
and the last element is excluded. But here, as everywhere in the package,
all Python details should be hidden from the user.)

```{r}
apply(getData(d1, c('1:4', '1:27998'), transfermode='JSON'), 1, sum)
apply(getData(d1, c('1:4', '1:27998'), transfermode='binary'), 1, sum)
print(getData(d2, c('1:9:3', '1:11:2')))
```



